---
title: "Ecotox Database Handling and Analysis"
output:
  html_document:
    df_print: paged
    code_folding: hide
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(beemixtox1)
library(tidyverse)
options(knitr.kable.NA = '')
```

## Data Pre-processing

### Query from EPA-Ecotox

The following filtering criteria was used to extract the relevant data form the EPA-Ecotox database. In this extraction, the dataset contains 576 CAS numbers. 

- **Chemicals**
- **Effect Measurements **
  - Mortality Group
	    - Mortality
- **Endpoints **
  - Concentration Based Endpoints
	  - LD50
- **Species **
  - Name(s) / Number(s)
	  - honey bee
  - Kingdom: Animals
  - Name Search Type: Common Name
- **Test Conditions **
  - Test Locations
	  - Lab
- **Publication Options **



```{r eval=FALSE}
#Define and set paths
Dir_Data = "~/Projects/beemixtox_public/data-raw/"
Data.SSD = read.csv(paste0(Dir_Data,"data/Copy of etc4373-sup-0002-supmat.csv"))
## usethis::use_data(Data.SSD) ## The common-name of the EPA Ecotox DB.
#Load data (USEPA internal not for publication)

#Load data

Data = read.csv(paste0(Dir_Data,"data/TerrestrialReport.csv"))
## usethis::use_data("Data")
length(unique(Data$CAS.Number))
#578 CAS
```

### Selection and Curation of the Raw Dataset

- Selection
    - Life stage: Adult
    - Duration days <=2, restrict to 24 h and 48 h studies.
    - Remove censored LDx. 
    - Use CASes with no less than 3 observations. 29 Chemicals
    - Retain only data with units in "AI mg/org","AI ng/org","AI ug/org","mg/bee","mg/org","ng/org","ug/bee","ug/org"
    - Exposure type: "Oral via capsule","Spray"
 

    

```{r eval=FALSE}
#Subset dataset for relevant parameters
Data.1 = Data
Data.1 = Data.1[Data.1$Organism.Lifestage%in%c("Adult"),]

#Subset for relevant exposure times
Data.1$Observed.Duration..Days.[Data.1$Observed.Duration..Days.=="NR"] = NA
Data.1$Observed.Duration..Days. = as.numeric(as.character(Data.1$Observed.Duration..Days.))

# Restrict to 24 h & 48 h end-points
Data.1 = Data.1[Data.1$Observed.Duration..Days.>=1 & Data.1$Observed.Duration..Days.<=2,]

#Restrict to definitive LDx
Data.1 = Data.1[Data.1$Observed.Response.Mean.Op%in%c(""),]

Data.1 = droplevels(Data.1)

length(unique(Data.1$CAS.Number))

# How many end-points per CAS number?
NPerCAS = aggregate(Observed.Response.Mean ~ CAS.Number, data =Data.1, length)
NPerCAS = NPerCAS[order(NPerCAS$Observed.Response.Mean, decreasing = T),]

# Restrict to more than 5 observations
NPerCAS = NPerCAS[NPerCAS$Observed.Response.Mean>=3,]
#29 compunts

# Restrict Data.1 for these 29 compounds
Data.1 = Data.1[Data.1$CAS.Number%in%c(NPerCAS$CAS.Number),]; Data.1 = droplevels(Data.1)

# Homogenize units
table(Data.1$Observed.Response.Units)

## UNITS
Data.1$Observed.Response.Mean = as.numeric(as.character(Data.1$Observed.Response.Mean))
# Retain only useful units
Data.1 = Data.1[Data.1$Observed.Response.Units%in%c("AI mg/org","AI ng/org","AI ug/org","mg/bee","mg/org","ng/org","ug/bee","ug/org"),]; Data.1 = droplevels(Data.1)

#Transform mg to microgram
Data.1$Observed.Response.Mean[Data.1$Observed.Response.Units%in%c("AI mg/org","mg/bee","mg/org")] = Data.1$Observed.Response.Mean[Data.1$Observed.Response.Units%in%c("AI mg/org","mg/bee","mg/org")]*1000 #to ug/bee
Data.1$Observed.Response.Units[Data.1$Observed.Response.Units%in%c("AI mg/org","mg/bee","mg/org")] = "ug/bee"

#ng to microgram
Data.1$Observed.Response.Mean[Data.1$Observed.Response.Units%in%c("AI ng/org","ng/org")] = Data.1$Observed.Response.Mean[Data.1$Observed.Response.Units%in%c("AI ng/org","ng/org")]/1000 #to ug/bee
Data.1$Observed.Response.Units[Data.1$Observed.Response.Units%in%c("AI ng/org","ng/org")] = "ug/bee"

# Homogenize ng/bee
Data.1$Observed.Response.Units[Data.1$Observed.Response.Units%in%c("AI ug/org","ug/bee","ug/org")] = "ug/bee"

table(Data.1$Observed.Response.Units)
Data.1 = droplevels(Data.1)

# Exposure media
table(Data.1$Exposure.Type)
Data.1 = Data.1[!Data.1$Exposure.Type%in%c("Oral via capsule","Spray"),]; Data.1 = droplevels(Data.1)
```

- Data Curation
    - Restrict the database for chemicals with repeated entries (i.e., more than 3 or 5 LD50 for the same chemical) ==> 16 chemicals
    - Units transformed to microgram based. (mg, ng ==> ug) Note this step is done in the previous code chunk. 



```{r eval=FALSE}
# Approximate variability
Bee.var.N = aggregate(Observed.Response.Mean ~ CAS.Number, data =Data.1, length)
Bee.var.Ave = aggregate(Observed.Response.Mean ~ CAS.Number, data =Data.1, mean)
Bee.var.sd = aggregate(Observed.Response.Mean ~ CAS.Number, data =Data.1, sd)

# Merge
Bee.var = merge(Bee.var.N,Bee.var.Ave, by="CAS.Number")
Bee.var = merge(Bee.var,Bee.var.sd, by="CAS.Number")
names(Bee.var) [c(2:4)] = c("N", "Mean", "sd")

# Restrict to at least 5 cases per CAS
Bee.var = Bee.var[Bee.var$N>3,] # 16 chemicals

Bee.var$CV.Perc = 100*(Bee.var$Mean/Bee.var$sd)
Bee.var = merge(Bee.var, Data.SSD[,c(1,3)], by.x = "CAS.Number", by.y = "CAS.", all.x = T)
Bee.var = Bee.var[order(Bee.var$N, decreasing = T),]

# Summary of CV%
summary(Bee.var)

# Check for independency of N and Mean
plot(Bee.var$N,Bee.var$CV.Perc)
plot(log10(Bee.var$N),Bee.var$CV.Perc)
plot(log10(Bee.var$Mean), Bee.var$CV.Perc)

# Which chemicals do we have represented?
```


```{r eval=FALSE}
#restrict Data.1 to the selected CAS.N
Data.2 = Data.1
Data.2 = Data.2[Data.2$CAS.Number%in%Bee.var$CAS.Number,]; Data.2 = droplevels(Data.2)
Data.2$CAS.Number = as.character(Data.2$CAS.Number)
```

- Check the consistency of the data. 
```{r}
# Check consistency again
table(Data.2$Chemical.Grade) %>% knitr::kable(.,caption ="Chemical Grade")%>% kableExtra::kable_classic_2()
# Chemical grade is not reported in most cases
table(Data.2$Organism.Lifestage)%>% knitr::kable(.,caption ="Organism Life Stage")%>% kableExtra::kable_classic_2()
table(Data.2$Exposure.Type)%>% knitr::kable(.,caption ="Exposure Type")%>% kableExtra::kable_classic_2()
table(Data.2$Number.of.Doses)%>% knitr::kable(.,caption ="Number of Doses")%>% kableExtra::kable_classic_2()
table(Data.2$Observed.Duration..Days.)%>% knitr::kable(.,caption ="Duration in Days")%>% kableExtra::kable_classic_2()
```


```{r eval=FALSE}
aov.1 = aov(Observed.Response.Mean ~ CAS.Number + Conc.1.Type..Author. + Exposure.Type + Observed.Duration..Days., data = Data.2)
summary(aov.1)


# Save reference list only
Data.2.Ref = unique(Data.2[,c(70,71,72,73,74)])
## usethis::use_data(Data.2)
## write.csv(Data.2.Ref, file = "Data.2.Ref_ECOTOX_BeeLD50_Curated.csv", row.names = F)
```

 


## Correlations among variables

In this section we we use EDA and ANOVA to check possible correlations among the variables.   

```{r fig.width=8}
Data.2 <- Data.2 %>% mutate(logTox = log(Observed.Response.Mean))
mod = lm(log(Observed.Response.Mean) ~ CAS.Number + Conc.1.Type..Author. + Exposure.Type + Observed.Duration..Days., data = Data.2)
summary(mod)
## car::Anova(mod) %>% pander::pander(.)
```

```{r}
car::Anova(mod) %>% knitr::kable(.,digits = 3) %>% kableExtra::kable_classic()
```


As shown in the ANOVA Table, none of the covariate variables, except for CAS,  has a significant effect on the observed response mean. 

From the EDA, we see the formulation has in general has higher observed response mean values as hown in Figure 1 and Figure 3. However, if we break it down to each CAS, the relationship does not hold for most of the CAS. Figure 4 confirmed our finding in the simple ANOVA analysis, the variance is mainly explained by the CAS difference, not by Conc types.  


```{r fig.width=8,fig.align="center",fig.cap=c("Figure 1: Paired Plot of the variable in the dataset", "Figure 2: Relationship between log of the Tox value and the duration of the study","Figure 3: logTox and CAS, concentration type, exposure type relationship")}
library(GGally)
ggpairs(Data.2[,c("logTox","Conc.1.Type..Author.","Exposure.Type","Observed.Duration..Days.")])
ggplot(data=Data.2,aes(x=Observed.Duration..Days.,y=log(Observed.Response.Mean)))+geom_point()+geom_boxplot(aes(group=Observed.Duration..Days.))

ldat <- Data.2 %>% dplyr::select(c(CAS.Number , Conc.1.Type..Author., Exposure.Type,logTox)) %>% pivot_longer(!logTox,names_to="variables",values_to="value") 
ggplot(ldat,aes(x=value,y=logTox))+geom_boxplot()+geom_point()+facet_wrap(~variables,scales = "free")+ theme(axis.text.x = element_text(angle = 90))
```



```{r fig.width=8,fig.align="center",fig.cap="Figure 4: CAS and Conc Type interaction"}
ggplot(Data.2,aes(x=Conc.1.Type..Author.,y=logTox))+geom_boxplot()+geom_point()+facet_wrap(~CAS.Number,scales = "free_y")+ theme(axis.text.x = element_text(angle = 90))
```
